\mythesistitleNOTSYNPOSIS \tnote[fyi]{Synopsis title is ``Generalization of Consecutive Ones Property of Binary Matrices''}

### 2012-01-29 src/030chap3.tex
- a whole bunch of cleanups. see diff. - removed problem defs from chap 1. they were duplicates from chap 3. - CODED FIGURES IN TIKZ. forbidden subgraphs, graphmatrix example graphs. - BEGAN CHAPTER 3 EDITS.
Formatting/layout changes
-------

- Added FrenchLayout to make lists denser
- Added hanging indent for Definitions
- Compressed theorem env's above below spaces
- Creaded env for problem definition minipages.
- moved all clearpage/page counter and other prechapter settings to the chapter tex files.
- Fixed the page number bug in draft printout. removed \fancyhf{} to avoid resetting page n

@@

This chapter documents all the new results obtained by us
in the area of tree path labeling of path hypergraphs which is the
parent problem addressed in this thesis.

Section~\ref{sec:myresearchintro} recalls the idea of tree path
labeling. The necessary preliminaries with definitions etc. are
presented in Section~\ref{ch:prelims}. Section~\ref{sec:feasible}
documents the characterization of a feasible path labeling for any
path labeling from any target trees. Section~\ref{sec:spltargettree}
describes two special cases where the target tree is of a particular
family of trees. The first one is shown to be equivalent to COP
testing in Section~\ref{sec:icpplicpia}. Section~\ref{sec:ksubdivstar}
discusses the second special case and presents a polynomial time
algorithm to find the tree path labeling of a given set system from a
given \kstar. Section~\ref{sec:norestraint} discusses the plain
vanilla version where the target tree has no restrictions and the
algorithm to find a feasible TPL, if any, in this case.

\section[Summary of problems]{Summary of Proposed Problems}
\label{sec:myresearchintro}
In Section~\ref{sec:motive} we see that consecutive-ones property and
its equivalent problem of interval labeling of a hypergraph is a
special case of the general problem of tree path labeling of path
hypergraphs.  The problem of consecutive-ones property testing can be
easily seen as a simple constraint satisfaction problem involving a
hypergraph or a system of sets from a universe. Every column (row) of
the binary matrix can be converted into a set of non-negative integers
which are the indices of the rows (columns) with {\un}s in that column
(row). When observed in this context, if the matrix has the COP on
columns (rows), a reordering of its rows (columns) will result in sets
that have only consecutive integers. In other words, the sets after
applying the COP row (column) permutation are intervals.  In this
form, one can see that this is indeed the problem of finding interval
assignments to the given set system \cite{nsnrs09} with a single
permutation of the universe (set of row or column indices for COP of
columns or rows, respectively) which permutes each set to an
interval. The result in \cite{nsnrs09} characterizes interval
assignments to the sets which can be obtained from a single
permutation of the universe. The cardinality of the interval
assigned to it must be same as the cardinality of the set, and the
intersection cardinality of any two sets must be same as the
intersection cardinality of the corresponding intervals. This is a
necessary and sufficient condition. \tnote{(ICPIA) put reference to
  survey chapter}

Naturally, intervals are paths from a tree with maximum degree
two. Thus the interval assignment problem can be generalized into path
assignment problem from any tree. We refer to this as the {\em tree
  path labeling problem of path hypergraphs}. This is analogous to the
interval labeling problem in literature \cite{kklv10} to interval
hypergraphs. To elaborate, the problem is defined as follows -- given
a hypergraph $\cF$ from universe (hypergraph vertex set) $U$ and a target tree
$T$, does there exist a bijection $\phi$ from $U$ to the vertices of $T$ such
that for each hyperedge when applied to its elements, $\phi$ gives a path on
$T$.  More formally, the problem definition is as defined by \CFTPL.

{\small
  \begin{minipage}[h]{5in}
    \vspace{2mm}
    {\large \CFTPL}\\
    \begin{tabular}[t]{l|l}
      \hline\\
      {\tt Input} & 
      \begin{minipage}[t]{\probdefwidth}
        A hypergraph $\cF$ with vertex set $U$ and a tree $T$.\\
      \end{minipage}\\

      {\tt Question} &
      \begin{minipage}[t]{\probdefwidth}
        Does there exist a set of paths $\cP$ from $T$ and a bijection
        $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns
        {\bf true} on $(\cF, T, \cl)$.
      \end{minipage}\\
    \end{tabular}
  \end{minipage}\\
}

@@

%\begin{tabular}[t]{c}
{\small
\begin{minipage}[h]{5in}
 % \begin{singlespace}
 \vspace{2mm}
 {\large \FTPL}\\
 \begin{tabular}[t]{l|l}
 \hline\\
    {\tt Input} & 
    \begin{minipage}[t]{\probdefwidth}
      A hypergraph $\cF$ with vertex set $U$, a tree $T$, a set of
      paths $\cP$ from $T$ and a
      bijection $\cl$~$:$~$\cF \rightarrow \cP$.\\
    \end{minipage}\\
    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a bijection $\phi$~$:$~$U \rightarrow V(T)$
      such that $\phi$ when applied on any hyperedge in $\cF$ will
      give
      the path mapped to it by the given tree path labeling $\cl$.\\
      { i.e., $\cl(S) = \{\phi(x) \mid x \in S\}$, for every hyperedge
        $S \in \cF$.}
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\
}
% \end{tabular}

@@

With respect to computing a feasible TPL, as suggested by \CFTPL
problem, we were unable to discover an efficient algorithm for
it. Hence we consider two special cases of the same -- namely, \CFTPLINT
and \CFTPLKTREE on special target trees, namely, intervals and \kstars,
respectively.  Section~\ref{sec:spltargettree} discusses these
problems.

{\small
  \begin{minipage}[h]{5in}
    % \begin{singlespace}
    \vspace{2mm}
    {\large \CFTPLINT}\\
    \begin{tabular}[t]{l|l}
      \hline\\
      {\tt Input} & 
      \begin{minipage}[t]{\probdefwidth}
        A hypergraph $\cF$ with vertex set $U$ and a tree $T$ with
        maximum degree 2.\\
      \end{minipage}\\
      {\tt Question} &
      \begin{minipage}[t]{\probdefwidth}
        Does there exist a set of paths $\cP$ from $T$ and a bijection
        $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns
        {\bf true} on $(\cF, T, \cl)$.
      \end{minipage}\\
    \end{tabular}
    % \end{singlespace}
  \end{minipage}\\
}

{\small
  \begin{minipage}[h]{5in}
    % \begin{singlespace}
    \vspace{2mm}
    {\large \CFTPLKTREE}\\
    \begin{tabular}[t]{l|l}
      \hline\\
      {\tt Input} & 
      \begin{minipage}[t]{\probdefwidth}
        A hypergraph $\cF$ with vertex set $U$ such that every
        hyperedge
        $S \in \cF$ is of cardinality at most $k+2$ and a {\kstar} $T$.\\
      \end{minipage}\\
      {\tt Question} &
      \begin{minipage}[t]{\probdefwidth}
        Does there exist a set of paths $\cP$ from $T$ and a bijection
        $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns
        {\bf true} on $(\cF, T, \cl)$.
      \end{minipage}\\
    \end{tabular}
    % \end{singlespace}
  \end{minipage}\\
}

\CFTPLINT is nothing but the consecutive-ones property testing
problem.

An algorithm for \CFTPL on general trees which is less efficient than
polynomial time is presented in
Section~\ref{sec:norestraint}. \tnote[minor]{put some more description
  here. refer WG11.}

\remove[minor]{We focus on the question of generalizing the notion of an
  ICPIA cite-nsnrs09 to characterize feasible path assignments.  We
  show that for a given set system $\cF$, a tree $T$, and an
  assignment of paths from $T$ to the sets, there is a feasible
  bijection between $U$ and $V(T)$ if and only if all intersection
  cardinalities among any three sets (not necessarily distinct) is
  same as the intersection cardinality of the paths assigned to them
  and the input runs a filtering algorithm (described in this paper)
  successfully.  This characterization is proved constructively and it
  gives a natural data structure that stores all the relevant feasible
  bijections between $U$ and $V(T)$.  Further, the filtering algorithm
  is also an efficient algorithm to test if a tree path labeling to
  the set system is feasible.  This generalizes the result in
  cite-nsnrs09.}

@@

This section states definitions and basic facts necessary in the scope
of this document.

\subsection{Hypergraph Preliminaries}

\begin{definition}[Set systems and hypergraphs] 
  \noindent 
  The set $\F \subseteq (2^{U} \setminus \emptyset)$ is a {\em set
    system} of a universe $U$ with $|U| = n$.  The {\em support} of a
  set system $\F$ denoted by $\supt{\cF}$\tnote[minor]{change all supp
    references to supt command} is the union of all the sets in $\F$;
  $supp(\F) = \bigcup_{S \in \F}S$. For the purposes of this paper, a
  set system is required to ``cover'' the universe; $ supp(\cF) = U$.

  \noindent
  A set system $\cF$ can also be visualized as a {\em hypergraph}
  whose vertex set is $supp(\cF)$ and hyperedges are the sets in
  $\cF$. This is a known representation for
  interval systems in literature \cite{bls99,kklv10}.  We extend this
  definition here to path systems. Due to the equivalence of set
  system and hypergraph in the scope of this paper, we drop the
  subscript $_H$ in the notation and refer to both the structures by
  $\cF$.

  \noindent
  The {\em intersection graph}\, $\bI(\cF)$ of a hypergraph
  $\cF$ is a graph such that its vertex set has a bijection to $\cF$
  and there exists an edge between two vertices \iff their
  corresponding hyperedges have a non-empty intersection \cite{mcg04}.

  \noindent 
  Two hypergraphs $\cF'$, $\cF''$ are said to be {\em isomorphic} to
  each other, denoted by $\cF' \cong \cF''$, \iff there exists a
  bijection $\phi: supp(\cF') \rightarrow supp(\cF'')$ such that for
  all sets $A \subseteq supp(\cF')$, $A$ is a hyperedge in $\cF'$ \iff
  $B$ is a hyperedge in $\cF''$ where $B = \{\phi(x) \mid x \in A\}$
  \cite{kklv10}, written as $B=\phi(A)$.  This is called {\em
    hypergraph isomorphism}.  
\end{definition}

\begin{definition}[Path Hypergraph from a Tree]
  The graph $T$ represents a {\em target tree} with same number of
  vertices as elements in $U$; $|V(T)|=|U|=n$.  A {\em path system}\,
  $\cP$ is a set system of paths from $T$; $\cP \subseteq \{P \mid P
  \subseteq V, \text{ } T[P] \text{ is a path} \}$.  This generalizes
  the fact, from the literature \cite{bls99,kklv10}, that intervals
  can be viewed as sub-paths of a path.

  \noindent
  If the intersection graphs of $\cF$ and $\cP$ (a path system) are
  isomorphic, $\bI(\cF) \cong \bI(\cP)$, then the associated bijection
  $\cl: \cF \rightarrow \cP$ due to this isomorphism is called a {\em
    path labeling} of the hypergraph $\cF$.\footnote{Note that there
    are two kinds of isomorphisms here.  One is the isomorphism of
    intersection graphs on $\cF$ and $\cP$, i.e. $\bI(\cF)$ and
    $\bI(\cP)$ respectively. Second is the isomorphism between the
    hypergraphs $\cF$ and $\cP$.}

@@

  \noindent
  \add{To illustrate further, let $\cg: V(\cF) \rightarrow V(\cP)$ be
    the above mentioned isomorphism where $V(\cF)$ and $V(\cP)$ are
    the vertex sets that represent the hyperedges for each hypergraph
    respectively, $V(\cF) = \{ v_S \mid S \in \cF\}$ and $V(\cP) = \{
    v_P \mid P \in \cP\}$. Then the path labeling $\cl$ is defined as
    follows: $\cl(S_1) = P_1$ iff $\cg (v_{S_1}) = v_{P_1}$.  Just to
    emphasize, for a path labeling $\cl$ of $\cF$ with $\cP$ as the
    path system, $\cF^\cl$ is same as $\cP$.  The path system $\cP$
    may be alternatively denoted in terms of $\cF$ and $\cl$ as
    $\cF^\cl$. In most scenarios in this paper, what is given are the
    pair $(\cF, \cl)$ and the target tree $T$; hence this notation
    will be used more often.}

  \noindent
  If $\cF \cong \cP$ where $\cP$ is a path system, then $\cF$ is
  called a {\em path hypergraph} and $\cP$ is called {\em path
    representation} of $\cF$. If this isomorphism is $\phi: supp(\cF)
  \rightarrow V(T)$, then it is clear that there is an {\em induced
    path labeling} $\cl_\phi: \cF \rightarrow \cP$ to the set system;
  $\cl_\phi(S) = \set{y \mid y = \phi(x), x \in S}$ for all $S \in
  \cF$. Recall that $supp(\cP) = V(T)$.

  \noindent
  \add{A graph} $G$ is a {\em path graph} if it is isomorphic to the
  intersection graph $\bI(\cP)$ of a path system $\cP$.  This
  isomorphism gives a bijection $\cl': V(G) \rightarrow
  \cP$. Moreover, for the purposes of this paper, we require that in a
  path labeling, $supp(\cP) = V(T)$.  If graph $G$ is also isomorphic
  to $\bI(\cF)$ for some hypergraph $\cF$, then clearly there is a
  bijection $\cl: \cF \rightarrow \cP$ such that $\cl(S) = \cl'(v_S)$
  where $v_S$ is the vertex corresponding to set $S$ in $\bI(\cF)$ for
  any $S \in \cF$. This bijection $\cl$ is called the {\em path
    labeling} of the hypergraph $\cF$ and the path system $\cP$ may be
  alternatively denoted as $\cF^\cl$.

  \noindent
  A path labeling $(\cF, \cl)$ is defined to be {\em feasible} if $\cF
  \cong \cF^\cl$ and this hypergraph isomorphism $\phi: supp(\cF)
  \rightarrow supp(\cF^\cl)$ induces a path labeling $\cl_\phi: \cF
  \rightarrow \cF^\cl$ such that $\cl_\phi = \cl$.  \add{In this
    work}, we are given as input $\cF$ and a tree $T$, and the
  question is whether there is a path labeling $\cl$ to a set of paths
  in $T$.  We refer to such a solution path system by $\cF^\cl$.  A
  path labeling $(\cF, \cl)$ is defined to be {\em feasible} if
  % $\cF \cong \cF^\cl$ and this
  there is a hypergraph isomorphism $\phi: supp(\cF) \rightarrow
  supp(\cF^\cl)=V(T)$ induces a path labeling $\cl_\phi: \cF
  \rightarrow \cF^\cl$ such that $\cl_\phi = \cl$.
\end{definition}

\begin{definition}[Overlap Graphs and Marginal Hyperedges]
  An {\em overlap graph}\, $\bO(\cF)$ of a hypergraph $\cF$ is a graph
  such that its vertex set has a bijection to $\cF$ and there exists
  an edge between two of its vertices \iff their corresponding
  hyperedges overlap. Two hyperedges $S$ and $S'$ are said to {\em
    overlap}, denoted by $S \overlap S'$, if they have a non-empty
  intersection and neither is contained in the other; $S \overlap S'
  \text{ \iff } S \cap S' \ne \emptyset, S \nsubseteq S', S'
  \nsubseteq S$. Thus $\bO(\cF)$ is a spanning subgraph of $\bI(\cF)$
  and not necessarily connected. Each connected component of
  $\bO(\cF)$ is called an {\em overlap component}.

  \noindent
  A hyperedge $S \in \cF$ is called {\em marginal} if for all $S'
  \overlap S$, the overlaps $S \cap S'$ form a single inclusion chain
  \cite{kklv10}. Additionally, if $S$ is such that it is contained in
  no other marginal hyperedge in $\cF$, then it is called {\em
    super-marginal}.
\end{definition}

\begin{definition}[$k$-subdivided star] 
  A {\em star} graph is a
  complete bipartite graph $K_{1,p}$ which is clearly a tree and $p$
  is the number of leaves. The vertex with maximum degree is called
  the {\em center} of the star and the edges are called {\em rays} of
  the star. A {\em $k$-subdivided star} is a star with all its rays
  subdivided exactly $k$ times. The definition of a {\em ray of a
    $k$-subdivided star} is extended to the path from the center to a
  leaf. It is clear that all rays are of length $k+2$.
\end{definition}

\temptext{ --- WG11 begin --- }

\remove[dire]{
A path assignment }% $\A$ to $\F$ is defined as a set assignment
% where second universe is the vertex set $V$ of a given tree $T$ and
% every second subset in the ordered pairs is a path in this
% tree. Formally, the definition is as follows. 
% \begin{align*}
%   \A = \{ (S_i,P_i) \mid S_i \in \F, P_i \subseteq V \text{
%     s.t. }T[P_i] \text{ is a path, } i \in I \}
% \end{align*}
% In other words, $P_i$ is the path on the tree $T$ assigned to $S_i$ in
% $\A$. As mentioned before for set systems, the paths cover the whole
% tree, i.e. $\bigcup_{i \in I}P_i = V$ \\

@@

\begin{definition}[Partially ordered sets]

Let $X$ be a partially ordered set with $\preccurlyeq$ being the
partial order on $X$.  $mub(X)$ represents an element in $X$ which is
a maximal upper bound on $X$.  $X_m \in X$ is a maximal upper bound of
$X$ if $\nexists X_q \in X$ such that $X_m
\preccurlyeq X_q$. 
\end{definition}

\noindent
The set $I$ represents the index set $[m]$. If index $i$ is used
without further qualification, it is meant to be $i \in I$. Any
function, if not defined on a domain of sets, when applied on a set is
understood as the function applied to each of its elements. i.e. for
any function $f$ defined with domain $U$, the abuse of notation is as
follows; $f(S)$ is used instead of $\hat f(S)$ where
$\hat f(S) = \{y \mid y = f(x), x \in S\}$. \\

\noindent
When refering to a tree as $T$ it could be a reference to the tree
itself, or the vertices of the tree. This will be clear from the
context.\\

\noindent
Finally, an in-tree is a directed rooted tree in which all edges are
directed toward to the root.

\temptext{ --- WG11 end --- }

@@

\tnote{\sc refer to Problem Defs here}
In this section we give an algorithmic characterization of the
feasibility of a tree path labeling.  Consider a path labeling $(\cF,
\cl)$ on the given tree $T$. We call $(\cF, \cl)$ an {\em Intersection
  Cardinality Preserving Path Labeling (ICPPL)} if it has the
following properties.

>>>>

\xclearpage

@@

This chapter documents all the new results obtained by us in the area
of tree path labeling of path hypergraphs which is the problem
addressed in this thesis. The organization of the chapter is as
follows.

Section~\ref{sec:myresearchintro} recalls the idea of tree path
labeling. The necessary preliminaries with definitions etc. are
presented in Section~\ref{ch:prelims}. Section~\ref{sec:feasible}
documents the characterization of a feasible path labeling from any
target trees. Section~\ref{sec:spltargettree} describes two special
cases where the target tree is of a particular family of trees. The
first one is shown to be equivalent to COP testing in
Section~\ref{sec:icpplicpia}. Section~\ref{sec:ksubdivstar} discusses
the second special case and presents a polynomial time algorithm to
find the tree path labeling of a given set system from a given
\kstar. Section~\ref{sec:norestraint} discusses the plain vanilla
version where the target tree has no restrictions and the algorithm to
find a feasible TPL, if any, in this case.

\section[Summary of problems]{Summary of Proposed Problems}
\label{sec:myresearchintro}
In Section~\ref{sec:motive} we see that consecutive-ones property and
its equivalent problem of interval labeling of a hypergraph is a
special case of the general problem of tree path labeling of path
hypergraphs. Moreover, Section~\ref{sec:icpiasurvey} describes how the
problem of consecutive-ones property testing can be easily seen as a
simple constraint satisfaction problem involving a hypergraph or a
system of sets from a universe. Every column (row) of the binary
matrix can be converted into a set of non-negative integers which are
the indices of the rows (columns) with {\un}s in that column
(row). When observed in this context, if the matrix has the COP on
columns (rows), a reordering of its rows (columns) will result in sets
that have only consecutive integers. In other words, the sets after
applying the COP row (column) permutation are intervals.  In this
form, one can see that this is indeed the problem of finding interval
assignments to the given set system with a single permutation of the
universe (set of row or column indices for COP of columns or rows,
respectively) which permutes each set to an interval. The result in
\cite{nsnrs09} (see Theorems~\ref{th:icpia2} and \ref{th:icpia1})
characterizes interval assignments to the sets which can be obtained
from a single permutation of the universe. The cardinality of the
interval assigned to it must be same as the cardinality of the set,
and the intersection cardinality of any two sets must be same as the
intersection cardinality of the corresponding intervals. This is a
necessary and sufficient condition.

Intervals are paths from a tree with maximum degree two. Thus the
interval assignment problem can be naturally generalized into path
assignment problem from any tree. We refer to this as the {\em tree
  path labeling problem of path hypergraphs}. This is analogous to the
interval labeling problem in literature \cite{kklv10} to interval
hypergraphs. In brief, the problem is defined as follows -- given a
hypergraph $\cF$ from universe $U$ (\ie hypergraph vertex set) and a
target tree $T$, does there exist a bijection $\phi$ from $U$ to the
vertices of $T$ such that for each hyperedge when $\phi$ is applied to
its elements it gives a path on $T$.  More formally, the problem
definition is given by \CFTPL.

\begin{problemdef}{\CFTPL}{A hypergraph $\cF$ with vertex set $U$ and
    a tree $T$.}
  Does there exist a set of paths $\cP$ from $T$ and a bijection
  $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns {\bf
    true} on $(\cF, T, \cl)$.
\end{problemdef}

@@

\begin{problemdef}{\FTPL}{A hypergraph $\cF$ with vertex set $U$, a
    tree $T$, a set of paths $\cP$ from $T$ and a bijection
    $\cl$~$:$~$\cF \rightarrow \cP$.}

  Does there exist a bijection $\phi$~$:$~$U \rightarrow V(T)$ such
  that $\phi$ when applied on any hyperedge in $\cF$ will give
  the path mapped to it by the given tree path labeling $\cl$.\\
  { i.e., $\cl(S) = \{\phi(x) \mid x \in S\}$, for every hyperedge $S
    \in \cF$.}
\end{problemdef}

@@

With respect to computing a feasible TPL, as suggested by \CFTPL
problem, we were unable to discover an efficient algorithm for
it. However, we consider two special cases of the same on special
target trees -- namely, \CFTPLINT and \CFTPLKTREE on intervals and
\kstars, respectively.  Section~\ref{sec:spltargettree} discusses
these problems and their polynomial time solutions.  \CFTPLINT is a
demonstrated to be the known problem of \COP testing. The polynomial
time solution to \CFTPLKTREE is a new result by us.

\begin{problemdef}{\CFTPLINT}{ A hypergraph $\cF$ with vertex set $U$
    and a tree $T$ with maximum degree 2.}

  Does there exist a set of paths $\cP$ from $T$ and a bijection
  $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns {\bf
    true} on $(\cF, T, \cl)$.  
\end{problemdef}

\begin{problemdef}{\CFTPLKTREE}{A hypergraph $\cF$ with vertex set $U$
    such that every hyperedge $S \in \cF$ is of cardinality at most
    $k+2$ and a {\kstar} $T$.}

  Does there exist a set of paths $\cP$ from $T$ and a bijection
  $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns {\bf
    true} on $(\cF, T, \cl)$.
\end{problemdef}

% \CFTPLINT is nothing but the consecutive-ones property testing
% problem.

An algorithm for \CFTPL on general trees which is less efficient than
polynomial time is presented in
Section~\ref{sec:norestraint}.

@@

This section describes ideas and terminologies necessary in this
chapter. Some of these may have been seen earlier in this document,
but is recalled for the sake of completeness of the chapter.

\subsection{Set systems and hypergraphs}
%\begin{definition}[Set systems and hypergraphs]

  The set $\F \subseteq (2^{U} \setminus \emptyset)$ is a {\em set
    system} of a universe $U$ with $|U| = n$.  The {\em support} of a
  set system $\F$ denoted by $\supt{\cF}$ is the union of all the sets
  in $\F$; $supp(\F) = \bigcup_{S \in \F}S$. For the purposes of this
  paper, a set system is required to ``cover'' the universe; $
  supp(\cF) = U$.
  \par
%  \noindent
  A set system $\cF$ can also be visualized as a {\em hypergraph}
  whose vertex set is $supp(\cF)$ and hyperedges are the sets in
  $\cF$. This is a known representation for
  interval systems in literature \cite{bls99,kklv10}.  We extend this
  definition here to path systems. Due to the equivalence of set
  system and hypergraph in the scope of this paper, we drop the
  subscript $_H$ in the notation and refer to both the structures by
  $\cF$.
  \par
%  \noindent
  The {\em intersection graph}\, $\bI(\cF)$ of a hypergraph
  $\cF$ is a graph such that its vertex set has a bijection to $\cF$
  and there exists an edge between two vertices \iff their
  corresponding hyperedges have a non-empty intersection \cite{mcg04}.
  \par
%  \noindent 
  Two hypergraphs $\cF'$, $\cF''$ are said to be {\em isomorphic} to
  each other, denoted by $\cF' \cong \cF''$, \iff there exists a
  bijection $\phi: supp(\cF') \rightarrow supp(\cF'')$ such that for
  all sets $A \subseteq supp(\cF')$, $A$ is a hyperedge in $\cF'$ \iff
  $B$ is a hyperedge in $\cF''$ where $B = \{\phi(x) \mid x \in A\}$
  \cite{kklv10}, written as $B=\phi(A)$.  This is called {\em
    hypergraph isomorphism}.  
%\end{definition}

\subsection{Path Hypergraph from a Tree}
%\begin{definition}[Path Hypergraph from a Tree]
  The graph $T$ represents a {\em target tree} with same number of
  vertices as elements in $U$; $|V(T)|=|U|=n$.  A {\em path system}\,
  $\cP$ is a set system of paths from $T$; $\cP \subseteq \{P \mid P
  \subseteq V, \text{ } T[P] \text{ is a path} \}$.  This generalizes
  the fact, from the literature \cite{bls99,kklv10}, that intervals
  can be viewed as sub-paths of a path.

%  \noindent
  If the intersection graphs of $\cF$ and $\cP$ (a path system) are
  isomorphic, $\bI(\cF) \cong \bI(\cP)$, then the associated bijection
  $\cl: \cF \rightarrow \cP$ due to this isomorphism is called a {\em
    path labeling} of the hypergraph $\cF$.\footnote{Note that there
    are two kinds of isomorphisms here.  One is the isomorphism of
    intersection graphs on $\cF$ and $\cP$, i.e. $\bI(\cF)$ and
    $\bI(\cP)$ respectively. Second is the isomorphism between the
    hypergraphs $\cF$ and $\cP$.}

@@

%  \noindent
  \add{To illustrate further, let $\cg: V(\cF) \rightarrow V(\cP)$ be
    the above mentioned isomorphism where $V(\cF)$ and $V(\cP)$ are
    the vertex sets that represent the hyperedges for each hypergraph
    respectively, $V(\cF) = \{ v_S \mid S \in \cF\}$ and $V(\cP) = \{
    v_P \mid P \in \cP\}$. Then the path labeling $\cl$ is defined as
    follows: $\cl(S_1) = P_1$ iff $\cg (v_{S_1}) = v_{P_1}$.  Just to
    emphasize, for a path labeling $\cl$ of $\cF$ with $\cP$ as the
    path system, $\cF^\cl$ is same as $\cP$.  The path system $\cP$
    may be alternatively denoted in terms of $\cF$ and $\cl$ as
    $\cF^\cl$. In most scenarios in this paper, what is given are the
    pair $(\cF, \cl)$ and the target tree $T$; hence this notation
    will be used more often.}

%  \noindent
  If $\cF \cong \cP$ where $\cP$ is a path system, then $\cF$ is
  called a {\em path hypergraph} and $\cP$ is called {\em path
    representation} of $\cF$. If this isomorphism is $\phi: supp(\cF)
  \rightarrow V(T)$, then it is clear that there is an {\em induced
    path labeling} $\cl_\phi: \cF \rightarrow \cP$ to the set system;
  $\cl_\phi(S) = \set{y \mid y = \phi(x), x \in S}$ for all $S \in
  \cF$. Recall that $supp(\cP) = V(T)$.

%  \noindent
  \add{A graph} $G$ is a {\em path graph} if it is isomorphic to the
  intersection graph $\bI(\cP)$ of a path system $\cP$.  This
  isomorphism gives a bijection $\cl': V(G) \rightarrow
  \cP$. Moreover, for the purposes of this paper, we require that in a
  path labeling, $supp(\cP) = V(T)$.  If graph $G$ is also isomorphic
  to $\bI(\cF)$ for some hypergraph $\cF$, then clearly there is a
  bijection $\cl: \cF \rightarrow \cP$ such that $\cl(S) = \cl'(v_S)$
  where $v_S$ is the vertex corresponding to set $S$ in $\bI(\cF)$ for
  any $S \in \cF$. This bijection $\cl$ is called the {\em path
    labeling} of the hypergraph $\cF$ and the path system $\cP$ may be
  alternatively denoted as $\cF^\cl$.

%  \noindent
  A path labeling $(\cF, \cl)$ is defined to be {\em feasible} if $\cF
  \cong \cF^\cl$ and this hypergraph isomorphism $\phi: supp(\cF)
  \rightarrow supp(\cF^\cl)$ induces a path labeling $\cl_\phi: \cF
  \rightarrow \cF^\cl$ such that $\cl_\phi = \cl$.  \add{In this
    work}, we are given as input $\cF$ and a tree $T$, and the
  question is whether there is a path labeling $\cl$ to a set of paths
  in $T$.  We refer to such a solution path system by $\cF^\cl$.  A
  path labeling $(\cF, \cl)$ is defined to be {\em feasible} if
  % $\cF \cong \cF^\cl$ and this
  there is a hypergraph isomorphism $\phi: supp(\cF) \rightarrow
  supp(\cF^\cl)=V(T)$ induces a path labeling $\cl_\phi: \cF
  \rightarrow \cF^\cl$ such that $\cl_\phi = \cl$.
%\end{definition}

\subsection{Overlap Graphs and Marginal Hyperedges}
%\begin{definition}[Overlap Graphs and Marginal Hyperedges]
  An {\em overlap graph}\, $\bO(\cF)$ of a hypergraph $\cF$ is a graph
  such that its vertex set has a bijection to $\cF$ and there exists
  an edge between two of its vertices \iff their corresponding
  hyperedges overlap. Two hyperedges $S$ and $S'$ are said to {\em
    overlap}, denoted by $S \overlap S'$, if they have a non-empty
  intersection and neither is contained in the other; $S \overlap S'
  \text{ \iff } S \cap S' \ne \emptyset, S \nsubseteq S', S'
  \nsubseteq S$. Thus $\bO(\cF)$ is a spanning subgraph of $\bI(\cF)$
  and not necessarily connected. Each connected component of
  $\bO(\cF)$ is called an {\em overlap component}.

%  \noindent
  A hyperedge $S \in \cF$ is called {\em marginal} if for all $S'
  \overlap S$, the overlaps $S \cap S'$ form a single inclusion chain
  \cite{kklv10}. Additionally, if $S$ is such that it is contained in
  no other marginal hyperedge in $\cF$, then it is called {\em
    super-marginal}.
%\end{definition}

\subsection{Miscellaneous}
%\begin{definition}[$k$-subdivided star] 
  A {\em star} graph is a
  complete bipartite graph $K_{1,p}$ which is clearly a tree and $p$
  is the number of leaves. The vertex with maximum degree is called
  the {\em center} of the star and the edges are called {\em rays} of
  the star. A {\em $k$-subdivided star} is a star with all its rays
  subdivided exactly $k$ times. The definition of a {\em ray of a
    $k$-subdivided star} is extended to the path from the center to a
  leaf. It is clear that all rays are of length $k+2$.
%\end{definition}

% A path assignment $\A$ to $\F$ is defined as a set assignment
% where second universe is the vertex set $V$ of a given tree $T$ and
% every second subset in the ordered pairs is a path in this
% tree. Formally, the definition is as follows. 
% \begin{align*}
%   \A = \{ (S_i,P_i) \mid S_i \in \F, P_i \subseteq V \text{
%     s.t. }T[P_i] \text{ is a path, } i \in I \}
% \end{align*}
% In other words, $P_i$ is the path on the tree $T$ assigned to $S_i$ in
% $\A$. As mentioned before for set systems, the paths cover the whole
% tree, i.e. $\bigcup_{i \in I}P_i = V$ \\

@@

%\begin{definition}[Partially ordered sets]

  Let $X$ be a partially ordered set with $\preccurlyeq$ being the
  partial order on $X$.  $X_m \in X$ is a maximal upper bound of $X$
  if $\nexists X_q \in X$ such that $X_m \preccurlyeq X_q$.  A maximal
  upper bound on $X$ is denoted by $mub(X)$.
  %represents an element in $X$ which is a maximal upper bound on $X$.
%\end{definition}

An {\em in-tree} is a directed rooted tree in which all edges are
directed toward to the root.

The set $I$ represents the index set $[m]$. If index $i$ is used
without further qualification, it is intended that $i \in I$.

@@

\tnote{\sc refer to Problem Defs here}
In this section we give an algorithmic characterization of the
feasibility of a tree path labeling.  
We focus on the question of generalizing the notion of an
  ICPIA cite-nsnrs09 to characterize feasible path assignments.  We
  show that for a given set system $\cF$, a tree $T$, and an
  assignment of paths from $T$ to the sets, there is a feasible
  bijection between $U$ and $V(T)$ if and only if all intersection
  cardinalities among any three sets (not necessarily distinct) is
  same as the intersection cardinality of the paths assigned to them
  and the input runs a filtering algorithm (described in this paper)
  successfully.  This characterization is proved constructively and it
  gives a natural data structure that stores all the relevant feasible
  bijections between $U$ and $V(T)$.  Further, the filtering algorithm
  is also an efficient algorithm to test if a tree path labeling to
  the set system is feasible.  This generalizes the result in
  cite-nsnrs09.

Consider a path labeling $(\cF,
\cl)$ on the given tree $T$. We call $(\cF, \cl)$ an {\em Intersection
  Cardinality Preserving Path Labeling (ICPPL)} if it has the
following properties.
